---
title: "The Fossil Fuel Lobby"
author: "Michael Waxman"
description: "Estimating the Monetary Resources of Certain Industries That Lobby on Environmental Issues"
output:
  distill::distill_article:
    self_contained: false
---

# Introduction
My main research question for this project is: "How do the monetary resources of certain industries who lobby on environmental issues compare with each other?". In this project, "certain industries" refers to the fossil fuel industry, environmental groups, and non-profits. I hypothesize that the fossil fuel industry has more monetary resources than environmental groups and non-profits. Given that the fossil fuel industry is a private sector industry, and a highly profitable industry, I expect the fossil fuel industry to have more money than environmental groups and non-profits who prioritize pushing forward environmental or social goals over turning a profit. 

I think this research question is interesting and important because if my hypothesis is correct, then we can begin to hypothesize the larger influence that the fossil fuel industry has on the political process compared to environmental groups and non-profits because lobbying is so incredibly intertwined with our political system and the groups with more money have a greater ability to lobby to push for specific public policies. This experiment can shed light on the disproportionate resources held by different industries who lobby on environmental issues. The next step, if my hypothesis is correct, would be to analyze how this money is used, which, if we see that the fossil fuel industry spends massive sums of money lobbying for looser environmental regulations, could help shed light on why the United States federal government failed to pass landmark climate change legislation for three decades despite scientific consensus about the existence of climate change and why there is still a lack of sustained and consistent climate action by the federal government on this issue. 

#Data: Loading in Data
```{r include = FALSE}
library(tidyverse)
lobby <- read_csv("Angelo's Data/cleaned_opensecrets-lobbying.csv")
library(dplyr)
```

# Data: Creating My Key Variables
```{r}
options(scipen = 9)

lobby <- lobby |>
  mutate(
    amount = extract_numeric(amount),
    log_amount = log(amount),
    i_fossilfuel = if_else(
      grepl("gas|oil|coal| oil|^oil",  indus_catname, ignore.case = TRUE) == TRUE,
      1, 0), 
    i_nonprofit = if_else(
      grepl("non.profit", indus_catname, ignore.case = TRUE) == TRUE,
      1, 0),
    i_environment = if_else(
      grepl("environment", indus_catname, ignore.case = TRUE) == TRUE,
      1, 0)
  ) |>
  filter(!is.infinite(log_amount)) |>
  select(bill_id, amount, log_amount, i_fossilfuel, i_nonprofit, i_environment, indus_catname) |> unique()
lobby |> select(indus_catname, matches("i_")) |> unique()
```
# Data: Outcome Distribution
```{r}
lobby |>
  ggplot(aes(x = amount)) +
  geom_histogram(aes(y = ..count../sum(..count..))) +
  scale_x_log10()
```
My project uses data from Open Secrets, the nation's premier research and government transparency group tracking money in politics and its effect on elections and policy. My cleaned dataset is a result of a series of mergers among Open Secrets datasets. I first joined Open Secrets data on lobbying issue areas with Open Secrets data on bills lobbied on and subsetted to environmental issues. Then I joined this dataset with opensecrets_crosswalk, which compiles data on lobby groups and their financial resources. This allowed me to see which lobby groups lobbied on which environmental bills and the financial resources of each lobby group. Then I joined this dataset with an Open Secrets industries dataset, which shows the type of industry each lobby group comes from. Thus, my cleaned dataset merges a few Open Secrets datasets to allow us to estimate the financial resources of different industries who lobby on environmental issues. 

The dependent variable for my experiment is monetary resources (measured in dollars). The independent variable for my experiment is industry type (fossil fuel, environmental, or non-profit). Both the independent and dependent variables are measured through accounting / record-keeping, and all of the data is found on the Open Secrets website. My research design is a cross-sectional observational study.

# Results: Bivariate Plot of Explanatory (x) and Outcome (y)
```{r}
lobby |>
  ggplot(aes(x = as.factor(i_fossilfuel), y = amount)) +
  geom_boxplot() +
  scale_y_log10()
```

# Results: Multivariate Regression
```{r}
regmodel <- lm(data = lobby, amount  ~ i_fossilfuel + i_nonprofit + i_environment)
summary(regmodel)$coefficients[1:4,] |> knitr::kable()
```

# Results
The main coefficient of interest in my regression is 329008.4, which is the coefficient for i_fossilfuel. This coefficient demonstrates that compared to other industries who lobby on environmental issues, the fossil fuel industry is positively correlated with having more monetary resources than other industries. The p-value of the estimated coefficient is 0.0000000, which means it is very unlikely that the result is due to chance, and we can reject the null hypothesis. I believe the coefficient represents correlation, not causation, because the coefficient is merely a measure of the relationship between being the fossil fuel industry and acquired monetary resources rather than an explanation of how being a company in the fossil fuel industry causes that company to have a certain sum of money. The latter argument would require a much more thorough investigation because there are many more variables involved in determining monetary a company's resources, including business history, balance sheets, macro-economic fluctuations, and more. 

I should also note that we have fixed effects in this experiment. 

# Conclusion
Whereas the fossil fuel industry is correlated with having more monetary resources compared to other industries that lobby on environmental issues, environmental lobbying organizations and nonprofits are correlated with having fewer monetary resources compared to other industries that lobby on environmental issues. I originally hypothesized that "the fossil fuel industry has more monetary resources than environmental groups and non-profits." My hypothesis is correct in this subset of data that is limited to interest group lobbying on environmental bills.

One limitation of my analysis is a lack of understanding of this disparity in monetary resources among different industries; further experimentation and analysis would need to be done to understand the causal mechanisms of my main conclusion. Another limitation of my analysis is the limited number of industries that I am comparing; this experiment would be more compelling if I had compared the monetary resources of several industries who lobby on environmental issues, rather than merely comparing the fossil fuel industry, environmental lobbying organizations, and nonprofits. 

One threat to inference in my experiment is a potential underestimate of environmental lobby groups' monetary resources; if I had added key terms such as "renewable," "alternative," or "clean" it is possible that I could have found more monetary resources in these industries, which are closely aligned with the goals of environmental lobby groups and would have closed some of the disparity between the monetary resources of the fossil fuel industry and environmental interest groups. 

My analysis could be improved by analyzing more industries, by more comprehensively defining my key industry variables (fossil fuel, environmental, and nonprofits) by adding more descriptive terms, and by doing more analysis—such as determining confidence intervals, z-scores, and other metrics—on the data to uncover different results from the data.